Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-05-09 docs/papers/roofline_model/gocean_roofline.tex
roofline: update stream2 results for desktop with effect of turbo/stepping

\begin{table}
\begin{tabular}{|l|c|c|c|c|}
\hline
  \multicolumn{5}{|c|}{E5-1620 v.2, 3.7GHz} \\
  \hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{28.32} \\
\hline
&  L1 Cache & L2 Cache & L3 Cache & Main memory \\
$n$-way set associative & 8    & 8   & 10 & -- \\
Size                  &   32 KB/core   & 256 KB/core   & 10 MB    &  -- \\
\hline
STREAM2 (GB/s)   &  160  &  61.0  & 46.0 &  20.5 \\
  \hline
\multicolumn{5}{|c|}{E5-2697 v.2, 2.7GHz}  \\
\hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{25.41} \\
\hline
               & L1 Cache & L2 Cache & L3 Cache & Main memory \\
$n$-way set associative & 8    & 8   & 20 & -- \\
Size           &   32 KB/core  & 256 KB/core   & 30 MB    &  -- \\
\hline
STREAM2 (GB/s) & 132      & 59.0     & 40.0     &  20.2 \\
\hline
\end{tabular}
\caption{The STREAM2 (DAXPY) and LINPACK benchmark results for a
  single thread running on each of the two CPUs considered here.}
\label{TAB_stream_linpack}
\end{table}

@@

Interpreting the results of the STREAM benchmark in order to get
bandwidth figures for all levels of the cache hierarchy is not
straightforward. We therefore used the STREAM2 benchmark which is
intended for this purpose. In Figure~\ref{FIG_stream2} we plot the
results obtained from the DAXPY component of the STREAM2 benchmark on
the E5-2697 CPU (using v.~14 {\bf (check this)} of the Intel
compiler. The plateaux in bandwidth for L2, L3 and main memory are
clear but that for L1 is considerably noisier. The final values we
have used in the roofline plots are given in
Table~\ref{TAB_stream_linpack}.

\begin{figure}
\includegraphics[width=120mm]{stream2_archer}
\caption{Results from running the STREAM2 benchmark on the E5-2697
  CPU.}
\label{FIG_stream2}
\end{figure}

 The equivalent results for the E5-1620 CPU are shown in
 Figure~\ref{FIG_daxpy_bw}. This plot has the same shape as that for
 the E5-2697 but is shifted upwards indicating an increase in
 bandwidth accross all levels of the cache hierarchy, but particularly
 for L3 and L1. In addition, the width of the plateau corresponding to
 the L3 cache is narrower because of the smaller size of this cache on
 the E5-1620.

\begin{figure}
\includegraphics[width=120mm]{daxpy_bw_perf}
\caption{Bandwidth obtained on the E5-1620 CPU by the original and
  modified versions of the daxpy kernel from the STREAM2 benchmark.}
\label{FIG_daxpy_bw}
\end{figure}

>>>>

\begin{table}
\begin{tabular}{|l|c|c|c|c|}
\hline
  \multicolumn{5}{|c|}{E5-1620 v.2, 3.7GHz} \\
  \hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{28.32} \\
\hline
&  L1 Cache & L2 Cache & L3 Cache & Main memory \\
$n$-way set associative & 8    & 8   & 10 & -- \\
Size                  &   32 KB/core   & 256 KB/core   & 10 MB    &  -- \\
\hline
STREAM2 (GB/s)   &  140  &  65.0  & 46.7 &  20.5 \\
  \hline
\multicolumn{5}{|c|}{E5-2697 v.2, 2.7GHz}  \\
\hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{25.41} \\
\hline
               & L1 Cache & L2 Cache & L3 Cache & Main memory \\
$n$-way set associative & 8    & 8   & 20 & -- \\
Size           &   32 KB/core  & 256 KB/core   & 30 MB    &  -- \\
\hline
STREAM2 (GB/s) & 132      & 59.0     & 40.0     &  20.2 \\
\hline
\end{tabular}
\caption{The STREAM2 (DAXPY) and LINPACK benchmark results for a
  single thread running on each of the two CPUs considered here.}
\label{TAB_stream_linpack}
\end{table}

@@

Interpreting the results of the STREAM benchmark in order to get
bandwidth figures for all levels of the cache hierarchy is not
straightforward. We therefore used the STREAM2 benchmark which is
intended for this purpose. In Figure~\ref{FIG_stream2_archer} we plot the
results obtained from the DAXPY component of the STREAM2 benchmark on
the E5-2697 CPU (using v.~14 {\bf (check this)} of the Intel
compiler. The plateaux in bandwidth for L2, L3 and main memory are
clear but that for L1 is considerably noisier. The final values we
have used in the roofline plots are given in
Table~\ref{TAB_stream_linpack}.

\begin{figure}
\includegraphics[width=120mm]{stream2_archer}
\caption{Bandwidth results from running the DAXPY component of the
  STREAM2 benchmark on the E5-2697 CPU.}
\label{FIG_stream2_archer}
\end{figure}

 The equivalent results for the E5-1620 CPU are shown in
 Figure~\ref{FIG_stream2_desktop}. This plot has the same shape as
 that for the E5-2697 but is shifted upwards indicating an increase in
 bandwidth accross all levels of the cache hierarchy, but particularly
 for L3 and L1. In addition, the width of the plateau corresponding to
 the L3 cache is narrower because of the smaller size of this cache on
 the E5-1620. Figure~\ref{FIG_stream2_desktop} also shows the effect
 on performance of disabling the turbo and frequency-stepping modes of
 the CPU. (Both sets of results are with hyper-threading disabled in
 order to reduce noise due to resource contention.) This reduces the
 performance obtained from the various levels of the cache hierarchy
 by a few percent but increases the bandwidth obtained to main-memory
 by a similar amount.

\begin{figure}
\includegraphics[width=120mm]{stream2_desktop}
\caption{Bandwidth results from running the DAXPY component of the
  STREAM2 benchmark on the E5-1620 CPU. Three data sets are plotted
  corresponding to three consecutive runs of the benchmark.}
\label{FIG_stream2_desktop}
\end{figure}

\begin{figure}
\includegraphics[width=120mm]{daxpy_bw_perf}
\caption{Bandwidth obtained on the E5-1620 CPU by the original and
  modified versions of the daxpy kernel from the STREAM2 benchmark.}
\label{FIG_stream2_daxpy}
\end{figure}
